\LARGE \bf Exploiting Non-Slip Wall Contacts \\ to Position Two Particles Using The Same Control Input

### 2018-10-13 journalWallFriction/resubmitv02/Response.tex

% difference between two pdf files: https://draftable.com/compare
% insert a pdf: https://tex.stackexchange.com/questions/8662/merge-two-pdf-files-output-by-latex
%   \usepackage{pdfpages}
%   \includepdf[pages=-]{ChangesFromV01toV02.pdf}
% gs -sDEVICE=pdfwrite -dCompatibilityLevel=1.4 -dNOPAUSE -dQUIET -dBATCH      -sOutputFile=ResponseCompressed.pdf Response.pdf
%
\documentclass[conference, onecolumn, 10pt]{../IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{times}

@@

		\begin{flushright}
		Aaron T.\ Becker\\Department of Electrical Engineering\\University of Houston\\Houston, TX 77004, USA\\Email: atbecker@central.uh.edu\\Web: youTube.com/aabecker5\\

		\today \vspace{.1cm} \\
		\end{flushright}

		#1\medskip\\

		Dear #2 Editorial Office,\medskip\\
		Please find attached the revised paper, #1, previously submitted as paper number 18-0277,
		along with the document containing a response to the reviewers. We are grateful to the reviewers for helping us improve our manuscript through their comments and questions. Please let us know if further information is required. This work extends the preliminary conference paper, ``\emph{Algorithms for shaping a particle swarm with a shared input by exploiting non-slip wall contacts}'', presented at the 2017 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS). The conference paper considered only square workspaces. This work extends the analysis to convex workspaces and 3D positioning. This paper also implements the algorithms using a hardware setup inspired by the anatomy of the gastrointestinal tract.\medskip
		\medskip

@@

		The new revision of our paper includes multi-media so that others can build on our results. These include illustrative videos for the simulations and experiments: 
	\begin{itemize}	 
 \item Video  \emph{01Model.mov} animates the concepts of uniform control inputs and non-slip boundary contacts.
 \item Video  \emph{02DeltaConfigurationSpace.mp4} demonstrates how the $\Delta$ configuration space (the configuration space showing the difference in position for two particles) is constructed for a variety of workspaces.
 \item Video  \emph{03SimulationWorkSpaces.mp4} shows demonstrations of motion planning in square and disc-shaped workspaces. 
 \item Video  \emph{04Hardware Experiments.mp4} shows an experiment trial moving two particles to goal positions in a small intestine phantom, then an experiment trial using cow stomach tissue.
		\end{itemize}

		   We also include four  Mathematica Notebooks (.nb files) containing the simulation code.  This code generates plots for the paper and animates the path planner algorithm for arbitrary inputs.
		   	\begin{itemize}	 
 \item   \emph{SquareWorkSpace.nb} generates paths in a square workspace for two particles.
 \item  \emph{CircularWorkSpace.nb} generates paths in a circular workspace for two particles.
 \item   \emph{DeltaConfigurationSpacePolygon.nb} generates the $\Delta$ configuration space for convex polygons
  \item   \emph{ShortestPathForADisk.nb} analytical solution for shortest path that touches a boundary from one position to another position in a circular workspace.
		\end{itemize}

		%   At the end of this letter, pages~\pageref{sec_lastpage}--\pageref{LastPage} is the revised manuscript, formatted so all changes can be easily identified by the reviewers, by using green colored text to indicate revised passages. 
		 The revised manuscript is formatted so all changes can be easily identified by the reviewers by using green colored text to indicate revised passages.

@@

	We made the model for both 2D and 3D more clear -- the particles are assumed to be neutrally buoyant so that the same force is applied to each particle.
	Please see the detailed responses below.

	\Reviewer{\#1}\response{This paper explains an underactuated control strategy for small teams
of magnetic microparticles which move under the influence of a single
broadcast signal. This underactuated control problem is relevant to
microrobotic swarms moving under magnetic field input. In previous
work, the authors have explored interesting control methods relying on
obstacles in the environment, but the case studied here is more
application-realistic. The control method here is clever and
successful. The work is interesting to read and I think that anyone
with a basic background in controls will find this work interesting.  
The main concept used here to achieve multi-particle control is that
the particles experience a no-slip condition when pushed against the
environment wall. The particles can be removed from the wall by pulling
them. 
The paper is an extension of an IROS2017 paper which introduced the
idea for square workspace only. This TRO submission generalizes to a
non-square workspace, which is a notable improvement. This version of
the work will thus be a helpful addition to the literature. 
The paper gives a very nice review of previous work in using broadcast
signals for multi-particle control.  }
	Thank you! We have completed a major revision, as explained below.

	\response{Is it expected that the no-slip condition will be a strongly satisfied
assumption for in-vivo biomedical applications? In cases where there
were some slip, how could that be handled?}

	To maintain clarity, this paper focused on systems with non-slip boundaries.  While several environments with non-slip boundaries exist (e.g. tripe, and intestines with villi), extending to lower friction values is an intriguing avenue that unfortunately does not fit within the 12 page limit for this journal, but is something we are investigating. The reachable sets with non-infinite friction are smaller. 
The conclusion now explains `` This paper assumed friction was sufficient to completely stop particles in contact with the boundary. The algorithms would require retooling to handle small friction coefficients."

@@

	Section IV-F: ``Workspaces that are tortuous or with many obstacles are better handled by other path
planners, such as RRT [29], or [5], which used collisions with protrusions of the workspace to rearrange particles.''.

	Also, during the hardware experiments, the particle that was pushed into the com stomach boundary disappeared from the camera, but control still was successful, indicating that perfect sensing is not necessary: ``Our algorithm successfully delivered the particles to goal positions in 5 out of 5 trials.''

	\response{Abstract: It is stated that ``given 3 orthogonal magnetic fields''.
This statement should be made more precise, because the magnetic
pulling here uses field gradients, not fields. In addition, these
gradients are not orthogonal. An accurate statement would need to be
more complex.}

	Yes.  To make this work as broadly applicable as possible (magnetic inputs are just one example) we changed the abstract to say ``This paper investigates particle control with uniform forces (the same force is applied everywhere in the workspace). Given a controllable field that can generate bidirectional forces in three orthogonal directions, steering one particle in 3D is trivial. ''

@@

	\response{A minor comment, sections IIIB and C are a little confusing since it
is not motivated why shortest path is being considered in the overall
argument of the paper.	Furthermore, it seems that shortest path in
IIIB is used for the situation moving two particles, while in IIIC it
is used for the situation of moving only one particle.	Consistency in
the presentation would help..}

	We rearranged the order because the optimization results can be applied to Alg. 1, but are not necessary to implement or understand the algorithm.  The results were combined into a new Section V, which opens by stating:

	``Algorithm 1 provided a technique to bring two particles to goal positions using global inputs, but did not optimize path length.   Changing the relative positions of particles in any workspace requires making one particle contact the boundary.
  In this section we present two results that can be incorporated into Algorithms 2 and 3 to generate shorter motion paths.''

%\label{sec_lastpage}\includepdf[pages=-]{ChangesFromV01toV02.pdf}

### 2018-10-13 journalWallFriction/Conclusion.tex
submitted v 02

  \section*{Appendix}\label{sec:appendix}
 The supplemental material includes four videos:
  	\begin{itemize}	 
 \item Video  \emph{01Model.mov} animates the concepts of uniform control inputs and non-slip boundary contacts.
 \item Video  \emph{02DeltaConfigurationSpace.mp4} demonstrates how the $\Delta$ configuration space (the configuration space showing the difference in position for two particles) is constructed for a variety of workspaces.
 \item Video  \emph{03SimulationWorkSpaces.mp4} shows demonstrations of motion planning in square and disc-shaped workspaces. 
 \item Video  \emph{04Hardware Experiments.mp4} shows an experiment trial moving two particles to goal positions in a small intestine phantom, then an experiment trial using cow stomach tissue.
		\end{itemize}	 	
We also include four  Mathematica Notebooks (.nb files) containing simulation code.  This code generates plots for the paper and animates the path planner algorithm for arbitrary inputs.
		   	\begin{itemize}	 
 \item   \emph{SquareWorkSpace.nb} generates paths in a square workspace for two particles.
 \item  \emph{CircularWorkSpace.nb} generates paths in a circular workspace for two particles.
 \item   \emph{DeltaConfigurationSpacePolygon.nb} generates the $\Delta$ configuration space for convex polygons
  \item   \emph{ShortestPathForADisk.nb} analytical solution for shortest path that touches a boundary from one position to another position in a circular workspace.
		\end{itemize}

>>>>

  \section*{Appendix}\label{sec:appendix}
 The supplemental material includes four videos:
  	\begin{itemize}	 
 \item Video  \emph{01Model.mov} animates the concepts of uniform control inputs and non-slip boundary contacts.
 \item Video  \emph{02DeltaConfigurationSpace.mp4} demonstrates how the $\Delta$ configuration space is constructed for a variety of workspaces.
 \item Video  \emph{03SimulationWorkSpaces.mp4} shows demonstrations of motion planning in square and disc-shaped workspaces. 
 \item Video  \emph{04Hardware Experiments.mp4} shows an experiment trial moving two particles to goal positions in a small intestine phantom, then an experiment trial using cow stomach tissue.
		\end{itemize}	 	
We also include four  Mathematica Notebooks (.nb files) containing simulation code.  
		   	\begin{itemize}	 
 \item   \emph{SquareWorkSpace.nb} generates paths in a square workspace for two particles.
 \item  \emph{CircularWorkSpace.nb} generates paths in a circular workspace for two particles.
 \item   \emph{DeltaConfigurationSpacePolygon.nb} generates the $\Delta$ configuration space for convex polygons
  \item   \emph{ShortestPathForADisk.nb} analytical solution for shortest path that touches a boundary from one position to another position in a circular workspace.
		\end{itemize}

### 2018-10-13 journalWallFriction/SwarmShapeControl.tex
updated response letter
Haoran's changes
submitted v 02

%\documentclass[conference]{IEEEtran}
\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts% This command is only needed if 
                                                          % you want to use the \thanks command
%\overrideIEEEmargins                                      % Needed to meet printer requirements.
\usepackage{times}

@@

Steered particles offer a method for targeted therapy, interventions, and drug delivery in regions inaccessible by large robots.
For example, magnetic actuation of particles has the benefits of requiring no tethers, being able to operate from a distance, and in some cases allows imaging for feedback (e.g. MRI).
 This paper investigates particle control with uniform forces (the same force is applied everywhere in the workspace).
%Given three orthogonal magnetic fields, steering one particle in 3D is trivial. 
Given a controllable field that can generate forces in three orthogonal directions, steering one particle in 3D is trivial. 
Adding additional particles to steer makes the system underactuated because there are more states than control inputs. 
However, the walls of \emph{in vivo} and artificial environments often have surface roughness such that the particles do not move unless actuation pulls them away from the wall.
In previous work, we showed that the individual 2D position of two particles is controllable using global inputs in a square workspace with non-slip wall contact \cite{shahrokhi2017algorithms}.
Because \emph{in vivo} environments are usually not square, this paper extends the previous work to all convex workspaces and to 3D positioning. 
We investigate analytically an idealized variant of this problem with non-slip boundaries and control inputs that are applied uniformly to all particles in the workspace.
This paper also implements the algorithms using a hardware setup inspired by the gastrointestinal tract.

% KEYWORDS:   
%Underactuated Robots
%Motion Control
%Path Planning for Multiple Mobile Robot Systems
%	
%This is an extension of work presented in a preliminary conference paper:
%S. Shahrokhi, A. Mahadev, and A. T. Becker, ÒAlgorithms for shaping a particle swarm with a shared input by exploiting non-slip wall contacts,Ó in Intelligent Robots and Systems (IROS), 2017 IEEE/RSJ International Conference on, 2017.
\end{abstract}

>>>>

% And here is the link to the videos and summary and read me:
%  https://www.dropbox.com/home/BoundaryInteractionVideos
% difference between two pdf files: https://draftable.com/compare
%\documentclass[conference]{IEEEtran}
\documentclass[letterpaper, 10 pt, conference]{ieeeconf}
\IEEEoverridecommandlockouts% This command is only needed if 
                                                          % you want to use the \thanks command
%\overrideIEEEmargins                                      % Needed to meet printer requirements.
\usepackage{times}

@@

Steered particles offer a method for targeted therapy, interventions, and drug delivery in regions inaccessible by large robots.
For example, magnetic actuation of particles has the benefits of requiring no tethers, being able to operate from a distance, and in some cases allows imaging for feedback (e.g. MRI).
 This paper investigates position control of particles using uniform forces (the same force is applied everywhere in the workspace).
Given a controllable field that can generate bidirectional forces in three orthogonal directions, steering one particle in 3D is trivial. 
Adding additional particles to steer makes the system underactuated because there are more states than control inputs. 
However, the walls of \emph{in vivo} and artificial environments often have surface roughness such that the particles do not move unless actuation pulls them away from the wall.
In previous work, we showed that the individual 2D position of two particles is controllable using global inputs in a square workspace with non-slip wall contact \cite{shahrokhi2017algorithms}.
Because \emph{in vivo} environments are usually not square, this paper extends the previous work to all convex workspaces and to 3D positioning. 
We investigate analytically an idealized variant of this problem with non-slip boundaries and control inputs that are applied uniformly to all particles in the workspace.
This paper also implements the algorithms using a hardware setup inspired by the gastrointestinal tract.

% KEYWORDS:   
% Underactuated Robots
% Motion Control
% Path Planning for Multiple Mobile Robot Systems
% Configuration Space
%	
%This is an extension of work presented in a preliminary conference paper:
%S. Shahrokhi, A. Mahadev, and A. T. Becker, ÒAlgorithms for shaping a particle swarm with a shared input by exploiting non-slip wall contacts,Ó in Intelligent Robots and Systems (IROS), 2017 IEEE/RSJ International Conference on, 2017.
\end{abstract}

### 2018-10-13 journalWallFriction/experiment.tex
submitted v 02

The intestine phantom model was used first and was made to mimic the geometry of an intestine and its villi. The model consists of a circular ring with an outer diameter of $\SI{50}{\milli\metre}$, an inner diameter of $\SI{46}{\milli\metre}$, and 60 $\SI{2}{\milli\metre}$ long protrusions on its inner surface cut out of $\SI{6}{\milli\metre}$ thick acrylic to model the geometry of intestinal villi. The top row of Fig.~\ref{fig:story}  shows one experiment. Starting and ending positions were printed beneath the workspace on transparency film. Our algorithm successfully delivered the particles to goal positions in 10 out of 10 trials.
A video showing one trial of this experiment is available in the supplementary materials.

>>>>

The intestine phantom model was used first and was made to mimic the geometry of an intestine and its villi.  To model the geometry of intestinal villi, the model consists of a circular ring cut out of $\SI{6}{\milli\metre}$ thick acrylic.  The ring has an outer diameter of $\SI{50}{\milli\metre}$, an inner diameter of $\SI{46}{\milli\metre}$, and sixty $\SI{2}{\milli\metre}$ long protrusions on its inner surface. The top row of Fig.~\ref{fig:story}  shows one experiment. Starting and ending positions were printed beneath the workspace on transparency film. Our algorithm successfully delivered the particles to goal positions in 10 out of 10 trials.
A video showing one trial of this experiment is available in the supplementary materials.
